The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-06 hw1/paper/main.tex
update PLA

\section{PLA}
  Assume that in a dataset $D$, there are two class labels. A perceptron will determine a data point with unknown class label by formula 
  \begin{equation}
    \rm{sign}(w^Tx)
  \end{equation}
  where $w$ is the weight

>>>>

\section{PLA}
  Assume that in a dataset $D$, there are two class labels, $0$ and $1$. A perceptron will determine a data point with unknown 
  class label by formula 
  \begin{equation}
    \rm{sign}(w^Tx)
  \end{equation}
  where $w$ is the weight, and the $\rm{sign}$ function is defined as 
  \begin{equation}
    \rm{sign}(x)=\begin{cases}1&,\rm{if }x>0\\0&,\rm{otherwise}\end{cases}
  \end{equation}
  The perceptron can update the weight dynamically by formula 
  \begin{equation}
    w_{t+1}\leftarrow w_t+y_{n(t)}x_{n(t)} \text{ when sign}(w^T_tx_{n(t)})\neq y_{n(t)}
  \end{equation}
  In \cite{gallant1990perceptron}, Gallant prove that if the dataset is linear separable, the perceptron learning algorithm will 
  eventually find a weight $w_T$ which satisfies $\rm{sign}(w^Tx_i)=y_i,\forall i$, in other words, $w_T$ can separate the dataset 
  by its class labels perfectly.
  In partice, the dataset is not always linear separable. Therefore, Gallant proposed a algorithm, PLA-pocket. Instead of find a 
  perfect weight, PLA-pocket picks a weight which minimize the errors in dataset.
